Template for indicator documentation

### 2023-09-11 DRAFT_functional_plant_indicators_natopen.Rmd
Update DRAFT_functional_plant_indicators_natopen.Rmd
some more minor changes

```{r}
head(ANO.sp.ind)
head(GRUK.species.ind)
head(NiN.natopen.cov)
```
For each ecosystem type with a NiN species list, we can calculate a community weighted mean (CWM) for the relevant functional plant indicators.
For semi-natural ecosystems, we are testing "Light", "Moisture", "Soil_reaction_pH", "Nitrogen", "Phosphorus", "Grazing_mowing", and "Soil_disturbance". In order to get distributions of CWMs rather than one single value (for comparison with the empirical testing data) the NiN lists can be bootstrapped.

>>>>

```{r}
head(ANO.sp.ind)
head(GRUK.species.ind)
head(NiN.natopen.cov)
```
For each ecosystem type with a NiN species list, we can calculate a community weighted mean (CWM) for the relevant functional plant indicators.
For semi-natural ecosystems, we are testing "Light", "Moisture", "Soil_reaction_pH", "Nitrogen", "Phosphorus", "Grazing_mowing", and "Soil_disturbance". In order to get distributions of CWMs rather than one single value (for comparison with the empirical testing data), the NiN lists can be bootstrapped.
